\textcolor{sage}{Does Hospital Leadership Matter? \newline Evidence from Pay-for-Performance}

### 2025-10-30 Slides/JobTalk(30minute).tex
Updates from Overleaf

        \item Unclear whether leadership matters when policies change incentives
    \end{enumerate}
\end{frame}

@@

\vspace{5mm} \large \pause

\begin{enumerate}
    \item \textbf{Hospital care makes up a third of health care spending} \scriptsize (\cite{cms2024nhe}) \normalsize

@@

    \begin{itemize}
        \item \normalsize Nonprofits drive the hospital industry \scriptsize (\cite{ASPE_2023}) \normalsize
    \end{itemize}

\vspace{8mm}

    \item \large \textbf{Policies often aim to improve the value of health care delivery}

@@

\begin{frame}{Pay-for-Performance Incentives}
    \large
    \begin{block}{\Large Main Takeaway:}
        \large 
        \centering
        \vspace{1mm}
        Hospitals now have financial incentives to improve quality

@@

\begin{frame}{Preview of Main Findings}

\textbf{Non-clinical executive teams respond more to financial incentives on quality}

\begin{wideitemize}
    \item Through readmission rates
    \item Non-clinical executive teams behave like profit-driven hospitals
\end{wideitemize}
\end{frame}

\begin{frame}{Contribution}
\large
    \textbf{Hospital Executives/Board of Directors}

    \begin{wideitemize}
        \item \normalsize Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
        \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
        \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
    \end{wideitemize}

    \vspace{5mm}\pause

    \textbf{Hospital Response to Pay-for-Performance}

    \begin{wideitemize}
        \item \normalsize Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts}) \normalsize
        \item Market concentration and systems affect response \scriptsize (\cite{kunz2024assessing}) \normalsize
        \item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
    \end{wideitemize}
\end{frame}

\begin{frame}{Rest of Talk}

    Setting and Data Collection

    About Executive Teams

    Theoretical Motivation

    Effect of Clinical Leadership

    Comparison to For-Profits

    Signaling vs. Managing
\end{frame}

@@

\vspace{4mm} \pause

@@

\hyperlink{executivejob}{\beamergotobutton{executive job}}

@@

\begin{frame}{Data Collection Process}
\begin{center}
\begin{tikzpicture}[
    node distance=3.1cm and 1.8cm,
    every node/.style={align=center, font=\normalsize},
    process/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=purple!30},
    output/.style={rectangle, draw, text centered, minimum width=2.7cm, minimum height=2.5cm, fill=purple},
    extract/.style={rectangle, draw, rounded corners, text centered, minimum width=2.5cm, minimum height=2cm, fill=sage!30},
    arrow/.style={thick, ->, >=stealth}
]

% Nodes
\node (step1) [process] {Hospital \\EINs};\pause
\node (step2) [process, right of=step1] {Download \\PDFs};
\draw[arrow] (step1) -- (step2); \pause
\node (step3) [process, right of=step2] {Extract\\text};
\draw[arrow] (step2) -- (step3); 
% New green box below step3
\node (extract) [extract, below of=step3, yshift=0.5cm] {Optical\\Character\\Recognition}; 
\draw[arrow] (extract) -- (step3);\pause
\node (step4) [process, right of=step3] {String\\cleaning\\algorithms};
\draw[arrow] (step3) -- (step4); \pause
\node (output) [output, right of=step4, text=white] {Executive\\Name\\Position\\Title};
\draw[arrow] (step4) -- (output);
\end{tikzpicture}
\end{center}
\end{frame}

@@

    \vspace{2mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

    \vspace{7mm}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}
\end{frame}

@@

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Fraction Int. Medicine Execs & 0.06 & 0.08 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for AMI + HF & 0.07 & 0.05 & 0.03\\
\hspace{1em}Penalized for AMI + Pneumonia & 0.02 & 0.02 & 0.02\\
\hspace{1em}Penalized for HF + Pneumonia & 0.41 & 0.40 & 0.33\\
\hspace{1em}Penalized for All Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

\begin{frame}{Hospital Objectives: Profit versus Patient Welfare}
    \Large
    \centering
    \begin{equation*}
        \max_{\theta}\hspace{2mm} \alpha\pi(\theta) + (1-\alpha)u(\theta)
    \end{equation*}
\end{frame}

@@

\begin{frame}{Choice of Quality}\label{choiceofquality}

@@

\large
    \begin{enumerate}
        \item If clinicians affect $\alpha$, they affect quality change after P4P

        \vspace{8mm}\pause
        \item If non-clinicians have higher $\alpha$, they act more like for-profits

        \vspace{8mm}\pause
        \item Mechanism could be revealing objectives or changing objectives
    \end{enumerate}
\end{frame}

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{``Synthetic DiD" type weights} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item No anticipation of incentive changes
    \item Stability in clinical executives not correlated with incentive change
\end{wideitemize}
\end{frame}

\begin{frame}{Average Team Changes Over Time}
\centering 
    \includegraphics[width=.8\textwidth]{Objects/change_means.pdf}
\end{frame}

@@

\begin{frame}{Mortality Rate}
    \begin{columns}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}
\end{frame}

\section{Signaling vs. Managing}

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Signaling vs. Managing}
\end{transitionframe}

\begin{frame}{Hypotheses}

\large
    \textbf{Clinical leaders represent underlying objectives ($\alpha$)}

    \begin{wideitemize}
        \item Timing of the clinical leader doesn't matter 
    \end{wideitemize}

    \textbf{Clinical leaders effectively change objectives ($\alpha$)}

    \begin{wideitemize}
        \item Timing of the clinical leader does matter
    \end{wideitemize}
\end{frame}

\begin{frame}{Estimation}
\large
    \begin{figure}[ht!]
\begin{center}

 \begin{tabular}{| m{15em} |}
 \hline \vspace{1mm}
 \textbf{Signaling:}\\ [0.5ex]
 \hline\hline 
 \vspace{2mm}
 Treat Group:  \hspace{15mm} Never MD \\
 \vspace{2mm}
 Comparison Group: \hspace{3mm} Ever MD  \\
 [1ex]
 \hline
 \end{tabular}
\hfil   %<---
 \begin{tabular}{|m{18em}|}
 \hline \vspace{1mm}
 \textbf{Managing:}\\ [0.5ex]
 \hline\hline
 \vspace{2mm}
 Treat Group: \hspace{11mm} MD in 2012 \\
 \vspace{2mm}
 Comparison Group:  MD not in 2012  \\
 [1ex]
 \hline
 \end{tabular}

\begin{frame}{Results}
    \begin{table}[ht!]
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Managing Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

    \textbf{Implications}
    \begin{itemize}
        \item Not all nonprofits have the same objectives
        \item More clinicians in leadership could shift objectives towards quality
    \end{itemize}

>>>>

        \item Unclear whether leadership matters when policies cause exogenous

        change in incentives
    \end{enumerate}
\end{frame}

@@

\vspace{10mm} \large \pause

\begin{enumerate}
    \item \textbf{Nonprofits drive the hospital industry} \scriptsize (\cite{ASPE_2023})

@@

    \begin{wideitemize}
        \item Mixed evidence about nonprofit behavior
    \end{wideitemize}
    \end{enumerate}
\end{frame}

%\begin{frame}{Addressing the Gaps}
    %\centering
    %\begin{tikzpicture}
        % First image (top-left)
        %\node[anchor=north west] (img1) at (0, 3) {\includegraphics[width=0.75\textwidth]{Graphics/nonprofit_screenshot1.png}};
        %\draw[line width=.45mm, lightcyan] (img1.north west) rectangle (img1.south east);

        % Second image (slightly down and right of the first image)
        %\node[anchor=north west] (img2) at (0, 0) {\includegraphics[width=0.75\textwidth]{Graphics/nonprofit_screenshot2.png}};
        %\draw[line width=.45mm, lightcyan] (img2.north west) rectangle (img2.south east);

    %\end{tikzpicture}
%\end{frame}

\vspace{18mm} \large

\begin{enumerate}
    \setcounter{enumi}{1}
    \item  \large \textbf{Policies often aim to improve the value of health care delivery}

@@

\begin{frame}{Pay-for-Performance Incentives}
    \large
    \begin{block}{\Large Main Takeaway of P4P:}
        \large 
        \centering
        \vspace{1mm}
        Hospitals now have financial incentives to improve quality

@@

% \begin{frame}{Contribution}
% \large
%     \textbf{Hospital Executives/Board of Directors}

% \vspace{2mm}

%     \begin{wideitemize}
%         \normalsize \item Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
%         \normalsize \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
%         \normalsize \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
%     \end{wideitemize}

%     \vspace{5mm}\pause

%     \textbf{Hospital Response to Pay-for-Performance}

% \vspace{2mm}

%     \begin{wideitemize}
%         \normalsize \item Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts})

%         \vspace{-.5mm}

%         \normalsize \item Market concentration and systems affect response 
%         \scriptsize (\cite{kunz2024assessing})

%         \normalsize\item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
%     \end{wideitemize}
% \end{frame}

@@

\vspace{3mm} \pause

@@

\hyperlink{executivejob}{\beamergotobutton{improving quality}}

@@

@@

    \vspace{1mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}

    \textbf{Years: 2009-2015}
\end{frame}

@@

\begin{frame}{Sample Definitions}
\centering
    \includegraphics[scale=.75]{Graphics/2010.png}
\end{frame}

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for two conditions & 0.50 & 0.47 & 0.38\\
\hspace{1em}Penalized for all Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

\begin{frame}{Hospital Objectives: Profit versus Patient Welfare}
    \Large
    \centering

    \begin{equation*}
        \max_{\theta}\hspace{2mm} \alpha\pi(\theta) + (1-\alpha)u(\theta)
    \end{equation*}

@@

\begin{frame}{Choice of Quality ($\theta$)}\label{choiceofquality}

@@

        \textbf{Response to P4P is tied to underlying objectives $\alpha$}
        \vspace{3mm}
        \begin{wideitemize}
            \item Ownership status is important to underlying objectives
            \item It's reasonable that priorities of leaders are also an important factor
        \end{wideitemize}

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{Weights based on outcomes pre-2012} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}\label{ident}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item Stability in clinical executives not correlated with incentive change \hyperlink{changes}{\beamergotobutton{analysis}}
\end{wideitemize}
\end{frame}

@@

\begin{frame}{Mortality Rate}\label{forprofmort}
    \begin{columns}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}

    \hyperlink{unobserved}{\beamergotobutton{unobserved}}
\end{frame}

\section{Unobserved}

@@

    \textbf{Implications}
    \begin{itemize}
        \item Despite all being nonprofits, hospitals with clinician leaders act more like we would expect nonprofits to
        \item In the absence of clinical leadership, nonprofits just act like for-profits
    \end{itemize}

### 2025-10-30 Slides/JobTalk(40minute).tex
Updates from Overleaf

    \begin{wideitemize}
        \item Mixed evidence about nonprofit behavior
    \end{wideitemize}
    \end{enumerate}
\end{frame}

@@

    \begin{wideitemize}
        \item \normalsize Unclear how leaders interact with this goal
    \end{wideitemize}

@@

% \begin{frame}{Contribution}
% \large
%     \textbf{Hospital Executives/Board of Directors}

% \vspace{2mm}

%     \begin{wideitemize}
%         \normalsize \item Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
%         \normalsize \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
%         \normalsize \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
%     \end{wideitemize}

%     \vspace{5mm}\pause

%     \textbf{Hospital Response to Pay-for-Performance}

% \vspace{2mm}

%     \begin{wideitemize}
%         \normalsize \item Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts})

%         \vspace{-.5mm}

%         \normalsize \item Market concentration and systems affect response 
%         \scriptsize (\cite{kunz2024assessing})

%         \normalsize\item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
%     \end{wideitemize}
% \end{frame}

@@

    \vspace{1mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}

    \textbf{Years: 2009-2015}
\end{frame}

@@

\begin{frame}{Sample Definitions}
\centering
    \includegraphics[scale=.75]{Graphics/2010.png}
\end{frame}

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for two conditions & 0.50 & 0.47 & 0.38\\
\hspace{1em}Penalized for all Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{Weights based on outcomes pre-2012} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}\label{ident}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item Stability in clinical executives not correlated with incentive change \hyperlink{changes}{\beamergotobutton{analysis}}
\end{wideitemize}
\end{frame}

@@

\begin{frame}{Mortality Rate}\label{forprofmort}
    \begin{columns}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.45\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}

    \hyperlink{unobserved}{\beamergotobutton{unobserved}}
\end{frame}

@@

@@

\begin{frame}{Average Team Changes Over Time}\label{changes}
\centering 
    \includegraphics[width=.8\textwidth]{Objects/change_means.pdf}
\end{frame}

    \hyperlink{ident}{\beamerreturnbutton{back}}

\begin{frame}{Driven by Unobserved Compositional Differences?}\label{unobserved}
\large

\vspace{3mm}
\begin{wideitemize}
    \item if true, we should see a difference in response no matter the timing of having a clinical executive
\end{wideitemize}
\end{frame}

\begin{frame}{Robustness Check}
\large
    \begin{figure}[ht!]
\begin{center}

\begin{frame}{Results}
    \begin{table}[ht!]
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Clinician Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\end{tabular}
\end{table}

\hyperlink{forprofmort}{\beamerreturnbutton{back}}
\end{frame}

>>>>

    \begin{wideitemize}
        \item \large Mixed evidence on nonprofit hospital behavior
    \end{wideitemize}
    \end{enumerate}
\end{frame}

@@

    \begin{wideitemize}
        \item \large Unclear how leaders interact with this goal
    \end{wideitemize}

@@

\begin{frame}{Preview of Main Findings}

\textbf{Non-clinical executive teams respond more to financial incentives on quality}

\begin{wideitemize}
    \item Through readmission rates
    \item Non-clinical executive teams behave like profit-driven hospitals
\end{wideitemize}
\end{frame}

\begin{frame}{Contribution}
\large
    \textbf{Hospital Executives/Board of Directors}

    \begin{wideitemize}
        \normalsize \item Physician board members $\implies$ lower public donations \scriptsize (\cite{brickley2010board}) \normalsize
        \normalsize \item No correlation b/w CEOs and hospital productivity in England \scriptsize (\cite{janke2019impact})\normalsize
        \normalsize \item Public hospitals in Chile improved when older physicians left CEO \scriptsize (\cite{otero2022managers}) \normalsize
    \end{wideitemize}

    \vspace{5mm}\pause

    \textbf{Hospital Response to Pay-for-Performance}

    \begin{wideitemize}
        \normalsize \item Hospitals decreased readmissions \scriptsize (\cite{gupta2021impacts})

        \vspace{-.5mm}

        \normalsize \item Market concentration and systems affect response 
        \scriptsize (\cite{kunz2024assessing})

        \normalsize\item Rewards had little impact on quality \scriptsize (\cite{norton2018moneyball}; \cite{friedson2019so})
    \end{wideitemize}
\end{frame}

@@

    \vspace{2mm}
    \begin{wideitemize}
        \item AHA
        \item Hospital Compare
        \item CMS Case Mix Index
        \item Health Care Cost Report Information System (HCRIS)
    \end{wideitemize}

    \vspace{7mm}

@@

    \begin{itemize}
        \item Manually match physician executives to NPPES NPI number
    \end{itemize}
\end{frame}

@@

\begin{frame}{Executive Teams}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
\toprule
 & Ever & Always & Never\\
  & Clinical Exec & Clinical Exec & Clinical Exec\\
\midrule
\addlinespace[0.3em]
Number Executives & 4.82 & 5.19 & 2.86\\
Fraction Clinical Execs & 0.20 & 0.26 & 0.00\\
Fraction Int. Medicine Execs & 0.06 & 0.08 & 0.00\\
Has a CMO & 0.55 & 0.52 & 0.07\\
Has Clinical CEO & 0.25 & 0.10 & 0.00\\
\addlinespace[0.6em]
Num. Hospitals & 452 & 62 & 385\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@

\begin{frame}{Hospital Statistics}\label{sumstats}
\vspace{-3mm}
\begin{table}[ht!]
\centering
\begin{tabular}[t]{lccc}
 & Ever & Always & Never\\
  & Clinical Exec &Clinical Exec &Clinical Exec\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Hospital Characteristics}}\\
\hspace{1em}Academic Med. Center & 0.41 & 0.51 & 0.20\\
\hspace{1em}Number Beds & 227 & 218 & 102\\
\hspace{1em}Physician Owned & 0.01 & 0.02 & 0.02\\
\hspace{1em}System Affiliated & 0.57 & 0.56 & 0.42\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Penalty/Payment Variables}}\\
\hspace{1em}Ever Received HVBP Incentive & 0.79 & 0.77 & 0.59\\
\hspace{1em}Penalized for one condition & 0.19 & 0.25 & 0.13\\
\hspace{1em}Penalized for AMI + HF & 0.07 & 0.05 & 0.03\\
\hspace{1em}Penalized for AMI + Pneumonia & 0.02 & 0.02 & 0.02\\
\hspace{1em}Penalized for HF + Pneumonia & 0.41 & 0.40 & 0.33\\
\hspace{1em}Penalized for All Conditions & 0.31 & 0.31 & 0.20\\
\bottomrule
\end{tabular}
\end{table}
\hyperlink{forprofitstats}{\beamergotobutton{for-profit stats}}
\end{frame}

@@

    Different methods:
    \begin{itemize}
        \item No weights
        \item \textbf{``Synthetic DiD" type weights} 
        \item Coarsened exact matching 
    \end{itemize}
\end{frame}

\begin{frame}{Identification Assumptions}

\large
\begin{wideitemize}
    \item Parallel trends
    \item No other 2012 event correlated with executive team and outcomes
    \item No hospital characteristics perfectly correlated with executive team
    \item No anticipation of incentive changes
    \item Stability in clinical executives not correlated with incentive change
\end{wideitemize}
\end{frame}

\begin{frame}{Average Team Changes Over Time}
\centering 
    \includegraphics[width=.8\textwidth]{Objects/change_means.pdf}
\end{frame}

@@

\begin{frame}{Mortality Rate}
    \begin{columns}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_md_synth_graph.pdf}
    \column{0.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{Objects/fp_mort_nomd_synth_graph.pdf}
    \end{columns}
\end{frame}

@@

\begin{transitionframe}
\centering \LARGE
    \textcolor{black}{Driven by Unobserved Compositional Differences?}
\end{transitionframe}

\begin{frame}{Driven by Unobserved Compositional Differences?}
\large

\vspace{3mm}
\begin{wideitemize}
    \item if true, difference in response should hold when timing of clinician changes
\end{wideitemize}
\end{frame}

\begin{frame}{Driven by Unobserved Compositional Differences?}
\large
    \begin{figure}[ht!]
\begin{center}

\begin{frame}{Results}
    \begin{table}[ht!]
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\underline{Weighted Avg. Readmission Rate}} & \multicolumn{2}{c}{\underline{Weighted Avg. Mortality Rate}} \\
 & (1) & (2) & (3) & (4)\\
\midrule
Signaling Effect & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
Clinician Effect &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
Observations & 3,005 & 1,595 & 3,005 & 1,595\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

@@
